Does It Scale? Static Output Approximation of PHP Web Applications Using Symbolic Execution

### 2017-01-11 paper.tex
completed sec 3

\subsection{Experience Report}
This sections sums up 
\textcolor{blue}{\blindtext}

@@

\begin{lstlisting}
<?php
function header_serif($title) {
   $style = "font-family: serif;";
   echo "<h1 style = '$style'>$title</h1>";
}
function header_sserif($title) {
   $style = "font-family: sans-serif;";
   echo "<h1 style = '$style'>$title</h1>";
}
\end{lstlisting}
	\caption{
		Function calls by indirect invocation mechanisms
		\label{fig:indirect_calls}
	}

@@

\subsection{Things We Tried\ldots}
\textcolor{blue}{\blindtext\blindtext}

>>>>

\subsection{Experience Report}
We identified a number of trade-offs between accuracy and performance that may
cause the approximation to be impractical, yet possible. Also, we identified
limitations impeding symbolic execution conceptually. For certain language
features, concrete information rather than symbolic values may be required to
actually be executed properly as this defective execution can impact subsequent
parts of the program which may become inaccessible and may be missed.

@@

\begin{lstlisting}
<?php
function header_serif($title) {
   $style = "font-family: serif;";
   echo "<h1 style = '$style'>$title</h1>";
}
function header_sserif($title) {
   $style = "font-family: sans-serif;";
   echo "<h1 style = '$style'>$title</h1>";
}

$font_style = mysql_result(...);
call_user_func('header_' . $font_style, 'Title');
\end{lstlisting}
	\caption{
		Function calls by indirect invocation mechanisms
		\label{fig:indirect_calls}
	}

@@

\subsubsection{Interpreter Customization}
We have approached issues we encountered in different ways, including
multiple-target method calls and foreach loops, as these represent a trade-off
between accuracy of execution and performance.
For method calls having ambiguous targets, we implemented different modes of
execution, ranging from a complete mode where a method is executed for all
possible targets to abstract modes with either a subset of targets or only a
single target. In the latter cases where targets are discarded, we assumed
symbolic values as method return values. Our symbolic interpreter can be
customized to work in the desired mode to scale accuracy or performance.
Nevertheless, for \sf{WordPress} these variations did not have significant
impact on the output approximation as symbolic execution was rather impeded by
dynamic features.
Also, for foreach loops we are able to toggle between a single iteration mode
and a complete iteration mode. Although we were able to increase code coverage
by accessing more code, it did not significantly increase our output
approximation.
Note that these variants have only been tested for \sf{WordPress} to better
understand possible trade-offs or simply achieve any output approximation in a
reasonable period of time. We believe based on our experience dynamic features
to be the main conceptual limitation impeding code coverage as well as output
approximation quality. In the next Section we analyze in detail the impact of
dynamic features with concrete foreach loop execution and complete
multiple-target execution for method calls.
